Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: included combined constraint to dcs section and table

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,amsfonts,amsmath,longbibliography]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
\usepackage{txfonts}
% \usepackage{newtxtext}
% \usepackage{newtxmath}
\usepackage{natbib}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\usepackage{mathrsfs}
\usepackage{makecell}
\usepackage{microtype}

@@

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & \dots \\
dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & \dots \\
cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
\emph{only parity-even corrections} and the second entries by considering
\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
$\lambda_{\rm e,o}$ are degenerate with the length scale $\ell$.
%
% \hs{Add a column with the constraint (if any) that we placed.}
% \hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
consider must be considered as an effective field theory, meaning it should be
considered valid only below an energy scale, or equivalently, a length scale.
%
As a cut-off length scale for the validity of the EFT we use,
%
\begin{equation}
\Lambda_{\rm EFT} (\varepsilon, \mathfrak{m}) = \varepsilon \, G \mathfrak{m} / c^2 \,,
\label{eq:def_cutoff}
\end{equation}
%
where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ is the median
value of one of the masses involved in the problem.
%
We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
dimensions of length and hence can be compared to the coupling strength $\ell$.
%
In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
but here we consider $\varepsilon \in [0, 1]$.
%
We will say that a bound has been placed on $\ell$, if most of the support of
the posterior distribution function $P(\ell)$ is in the interval
$[0, \, \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})]$.
%
In practice, this can be quantified through the cumulative distribution function
(CDF) associated to the marginalized posterior distribution $P(\ell)$,
%
\begin{equation}
P(\ell \leqslant \ell') = \int_{-\infty}^{\,\ell'} P(\ell') \, \dd \ell'\,.
\label{eq:def_cdf}
\end{equation}
%
For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that,
%
\begin{equation}
% \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,,
\label{eq:eft_bound}
\end{equation}
%
and likewise for other percentiles.

@@

@@

In Fig.~\ref{fig:dcs_cdf} we show the cumulative distribution function (CDF) as
evaluates with Eq.~\eqref{eq:def_cdf}, with $\ell' = \Lambda_{\rm EFT}$,
for both GW150914 (top panel) and GW200129 (bottom panel), where $\Lambda_{\rm EFT}$
is calculated with either $\mathfrak{m} = m_2$ (blue curves) or $M_{f}$ (orange curves),
and with $\varepsilon \in [0,\, 1]$.
%
For GW150914, we see that with $\gm = m_2$ that Eq.~\eqref{eq:eft_bound} is not
satisfied unless $\varepsilon \approx 0.9$ (with only $j=0$ corrections) and
$\varepsilon \approx 0.7$ (with both $j=0$ and $1$ corrections).
%
The situation is different if we use $\gm = M_f$. In this case, we find that
with or without spin corrections that Eq.~\eqref{eq:eft_bound} can be satisfied
with $\varepsilon \leq 1/2$, i.e., below the criteria used
Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
%
This means that with our model's assumptions and using the remnant's source mass $M_f$ to set the
cut-off scale that we can claim an upper bound
%
\begin{equation}
\ell_{\rm CS} \leqslant 46.5~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
\quad \textrm{at 90\% credibility},
\end{equation}
%
on dCS gravity and would constitute the first bound on this theory with
gravitational-wave observations alone.
%
We also note that since the CDF grows fast in approximate domain $\varepsilon = [0.2, 0.4]$,
that a stronger, albeit at lower credibility,
%
\begin{equation}
\ell_{\rm CS} \leqslant 27.4~\textrm{km}~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
\quad \textrm{at 68\% credibility},
\end{equation}
%
can also be placed, when we include the $j=1$ QNM correction.

We can draw qualitatively similar conclusions from the GW200129 event.
In particular, we find,
%
\begin{equation}
\ell_{\rm CS} \leqslant 43.9~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
\quad \textrm{at 90\% credibility},
\end{equation}
%
and
%
\begin{equation}
\ell_{\rm CS} \leqslant 19.3~\textrm{km}~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
\quad \textrm{at 68\% credibility},
\end{equation}
%
when we include the $j=1$ QNM correction.

These slightly stronger bound are a consequence of the larger support for $\ell_{\rm CS} \lessapprox 15$~km
for GW200129 (compare the top and middle panels in Fig.~\ref{fig:dCS_exec_sum}), and in part due to
the smaller median remmant ($M_{f} \approx 59.5\msun$ versus $M_{f} \approx 61.8\msun$ for GW150914).

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
%
In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
in spin QNM correction.
}
\label{fig:dCS_exec_sum}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$
as a function of the parameter $\varepsilon$ for both $\gm = m_2$ (blue curves), the secondary's source mass,
and $\gm = M_{f}$ (orange curves), the remnant's source mass, without (solid curve) and with (dashed curves)
linear in spin QNM corrections. The horizontal lines lay at 0.68 and 0.90.
%
We see that the CDF at $\varepsilon = 1/2$ is approximately one when $\gm =
M_{f}$ for both events, with and without including the $j = 1$ dCS corrections
to the dominat QNM.
}
\label{fig:dcs_cdf}
\end{figure}

\begin{table}[h]
\begin{tabular}{l l c c c}
\hline
\hline
Event & $j$ & Eq.~\eqref{eq:eft_bound}? & Eq.~\eqref{eq:parspec_bound}?  & Bound \\
\hline
GW150914 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant \dots$~km \\
GW150914 & $j = 0, 1$ & Yes & No  & --                                 \\
GW200129 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant \dots$~km \\
GW200129 & $j = 0, 1$ & Yes & No  & --                                 \\
\hline
\hline
\end{tabular}
\caption{Detailed summary of our results for dCS gravity.
%
We assume $\varepsilon = 1/2$.}
\end{table}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
\caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
The posterior shows that information was gained on this parameter relative to
the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
%
The vertical lines represent two threshold for the validity of the theory as
an EFT.
%
The dotted line (labeled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
%
The dot-dashed line (labeled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.
%
For both, we used $\varepsilon = 0.5$.
%
If we take the latter as a length scale for the validity of dCS as an EFT, we
have place upper bound on $\ell_{\rm CS} \leqslant 43.8$~km, within the
approximation of our formalism.
}
\label{fig:dCS_bounds}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_gamma_GW200129.pdf}
\caption{Posterior probability distribution on $\gamma_{\rm CS}$ with GW200129.
The posterior shows that the parameter $\gamma$ [see Eq.~\eqref{eq:def_gamma}]
in dynamical Chern-Simons has a peak at zero, indicating consistency with GR.
}
\label{fig:dCS_gamma_plot}
\end{figure}

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihaylov,
Serguei~Ossokine, and Helvi~Witek for discussions.
%
We also thank the computational resources provided by the AEI, specifically the
{\sc Hypatia} cluster and Steffen Grunewald for assistance.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%

>>>>

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,amsfonts,amsmath,longbibliography]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{bm}
\usepackage{txfonts}
% \usepackage{newtxtext}
% \usepackage{newtxmath}
\usepackage{natbib}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\usepackage{mathrsfs}
\usepackage{makecell}
\usepackage{microtype}

@@

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & \dots \\
EdGB      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
only parity-even corrections and the second entries by considering
only parity-odd corrections.
%
In these cases, the dimensionless parameters $\lambda_{\rm e,o}$ are degenerate
with the length scale $\ell$.
%
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
consider must be considered as an effective field theory, meaning it should be
considered valid only below an energy scale, or equivalently, a length scale.
%
As a cut-off length scale for the validity of the EFT we use,
%
\begin{equation}
\Lambda_{\rm EFT} (\varepsilon, \mathfrak{m}) = \varepsilon \, G \mathfrak{m} / c^2 \,,
\label{eq:def_cutoff}
\end{equation}
%
where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ is the median
value of one of the masses involved in the problem.
%
We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
dimensions of length and hence can be compared to the coupling strength $\ell$.
%
In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
but here we consider $\varepsilon \in [0, 1]$.
%
We will say that a bound has been placed on $\ell$, if most of the support of
the posterior distribution function $P(\ell)$ is in the interval
$[0, \, \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})]$.
%
In practice, this can be quantified through the cumulative distribution function
(CDF) associated to the marginalized posterior distribution $P(\ell)$,
%
\begin{equation}
P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} P(\ell') \, \dd \ell'\,.
\label{eq:def_cdf}
\end{equation}
%
For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that,
%
\begin{equation}
% \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,,
\label{eq:eft_bound}
\end{equation}
%
and likewise for other percentiles.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
%
In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
in spin QNM correction.
%
We stress that posteriors obtained including $j=1$ corrections, violated conditions~\eqref{eq:parspec_bound}
and therefore should not be used to draw meaningful conclusions. We show them for illustrative purposes
and also to emphasize the importance of taking conditions~\eqref{eq:eft_bound} and~\eqref{eq:parspec_bound}
simultaneously into consideration when analyzing the results of the parameter estimation.
}
\label{fig:dCS_exec_sum}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the
cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$ as a function of the parameter $\varepsilon$ for both
$\gm = m_2$ (solid and dashed lines) and $\gm = M_{f}$ (dot-dashed and dotted lines) without
(blue lines) and with (orange lines) linear-in-spin QNM corrections.
The horizontal lines lay at 0.68 and 0.90.
%
We see that the CDF curves for $\gm = M_{f}$ are above 90\% for $\varepsilon =
1/2$ for both events, with and without including the $j = 1$ dCS corrections to
the dominant QNM.
}
\label{fig:dcs_cdf}
\end{figure}

@@

In Fig.~\ref{fig:dcs_cdf} we show the cumulative distribution function (CDF) as
evaluates with Eq.~\eqref{eq:def_cdf}, with $\ell_{\rm max} = \Lambda_{\rm EFT}$,
for both GW150914 (top panel) and GW200129 (bottom panel), where $\Lambda_{\rm EFT}$
is calculated with either $\mathfrak{m} = m_2$ (blue curves) or $M_{f}$ (orange curves),
and with $\varepsilon \in [0,\, 1]$.
%
For GW150914, we see that with $\gm = m_2$ that Eq.~\eqref{eq:eft_bound} is not
satisfied unless $\varepsilon \approx 0.9$ (with only $j=0$ corrections) and
$\varepsilon \approx 0.7$ (with both $j=0$ and $1$ corrections).
%
The situation is different if we use $\gm = M_f$. In this case, we find that
with or without spin corrections that Eq.~\eqref{eq:eft_bound} can be satisfied
with $\varepsilon \leqslant 1/2$, i.e., below the criteria used
Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
%
This means that with our model's assumptions and using the remnant's source mass $M_f$ to set the
cut-off scale that we can claim an upper bound
%
\begin{equation}
\ell_{\rm CS} \leqslant 42.6~\textrm{km}
% ~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
\quad \textrm{(90\% credibility)},
\end{equation}
%
on dCS gravity and would constitute the first bound on this theory with
gravitational-wave observations alone.
%
We also note that since the CDF grows fast in approximate domain $\varepsilon = [0.2, 0.4]$,
that a stronger, albeit at lower credibility,
%
\begin{equation}
\ell_{\rm CS} \leqslant 37.4~\textrm{km}
% ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
\quad \textrm{at 68\% credibility},
\end{equation}
%
can also be placed, when $j=0$.

We can draw qualitatively similar conclusions from the GW200129 event.
In particular, we find,
%
\begin{equation}
\ell_{\rm CS} \leqslant 36.6~\textrm{km}
% 43.9~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
\quad \textrm{(90\% credibility)},
\end{equation}
%
and
%
\begin{equation}
\ell_{\rm CS} \leqslant 29.1~\textrm{km}
% ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
\quad \textrm{(68\% credibility)},
\end{equation}
%
when $j=0$.
%
These stronger bound are a consequence of the larger support for $\ell_{\rm CS} \lessapprox 15$~km
for GW200129 (compare the top and middle panels in Fig.~\ref{fig:dCS_exec_sum}), and in part due to
the smaller median remnant ($M_{f} \approx 59.5\msun$ versus $M_{f} \approx 61.8\msun$ for GW150914).

We also found for both GW events, that the
perturbative-conditions~\ref{eq:parspec_bound} imposed by the {\sc Parspec}
formalism are violated for the $\gamma_{\rm CS} \delta \tau^{(1)}$ coefficient.
%
This means that we cannot use these posterior to infer any meaningful bound on dCS gravity.
%
Now, since both event individually led to a bound on $\ell_{\rm CS}$ (assuming a cut-off scale for $\gm = M_{f}$
and $j = 0$), we can combine the posteriors to obtain the cumulative bound,
%
\begin{equation}
\ell_{\rm CS} \leqslant 34.5~\textrm{km}
\quad \textrm{(90\% credibility)},
\end{equation}
%
which is the main result of this section.
%
This bound is approximately a factor of four weaker than that placed by
Ref.~\cite{Silva:2020acr}, but
%
(i) relies only on GW observations and
%
(ii) suggests that a ringdown analysis can potentially place constraints on
theories which evade GW tests using inspiral information alone, such as the
case of dCS gravity~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
%
In Table~\ref{tab:summary_dcs} we summarize our findings of this section.

\begin{table}[h]
\begin{tabular}{l l c c c}
\hline
\hline
Event & $j$ & Eq.~\eqref{eq:eft_bound}? & Eq.~\eqref{eq:parspec_bound}?  & Bound ($\gm = M_{f}$) \\
\hline
GW150914 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant 46.5$~km \\
GW150914 & $j = 0, 1$ & Yes & No  & --                                 \\
GW200129 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant 43.9$~km \\
GW200129 & $j = 0, 1$ & Yes & No  & --                                 \\
Combined & $j = 0$    & Yes & Yes & \cellcolor{blue!10}$\ell_{\rm CS} \leqslant 34.5$~km \\
Combined & $j = 0, 1$ & Yes & No  & --                                 \\
\hline
\hline
\end{tabular}
\caption{Detailed summary of our results for dCS gravity for GW150914, GW200129, and
combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
%
We found that while our posteriors satisfy the condition~\eqref{eq:eft_bound} (with $\varepsilon = 1/2$),
they do not obey the condition~\eqref{eq:parspec_bound} for $j = 1$. This means
that our results for $j=0$ are the only ones we can confidently quote.
%
The combined bound, which is also quoted in Table~\ref{tab:ref_theories_qnms},
is $\ell_{\rm CS} \leqslant 34.5$~km.
}
\label{tab:summary_dcs}
\end{table}

@@

% \begin{figure}[t]
% \includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
% \caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
% The posterior shows that information was gained on this parameter relative to
% the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
% %
% The vertical lines represent two threshold for the validity of the theory as
% an EFT.
% %
% The dotted line (labeled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
% given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
% %
% The dot-dashed line (labeled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
% given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.
% %
% For both, we used $\varepsilon = 0.5$.
% %
% If we take the latter as a length scale for the validity of dCS as an EFT, we
% have place upper bound on $\ell_{\rm CS} \leqslant 43.8$~km, within the
% approximation of our formalism.
% }
% \label{fig:dCS_bounds}
% \end{figure}
%
% \begin{figure}[t]
% \includegraphics[width=\columnwidth]{figs/dcs_gamma_GW200129.pdf}
% \caption{Posterior probability distribution on $\gamma_{\rm CS}$ with GW200129.
% The posterior shows that the parameter $\gamma$ [see Eq.~\eqref{eq:def_gamma}]
% in dynamical Chern-Simons has a peak at zero, indicating consistency with GR.
% }
% \label{fig:dCS_gamma_plot}
% \end{figure}

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihaylov,
Serguei~Ossokine, Scott~E.~Perkins, and Helvi~Witek for discussions.
%
We also thank the computational resources provided by the AEI, specifically the
{\sc Hypatia} cluster and Steffen Grunewald for assistance.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%
